MSCI 718 Mini-Project: COVID-19 Time Series Analysis and Visualization

### 2020-04-23 MSCI718 2020W Project v3.Rmd
proofread

In addition to our report analysis, we have created an interactive visualization dashbord of the map of the world, through Rshiny. This dashboard contains 2 main components:
1) For a given date, the cumulative amount of *Deaths*, *Recoveries*, and *Confirmed Cases* in magnitude is indicated by a red circle for each country.
2) For a specific country chosen from the drop-down list, we display 4 graphs: Confirmed Cases, Trajectory of Confirmed Cases, Deaths, and a Forecast for the Future Number of Cases (indicated in blue from April 22 onwards).

>>>>

In addition to our report analysis, we have created an interactive visualization dashbord of the map of the world, through Rshiny. This dashboard contains 2 main components:

1) For a given date, the cumulative amount of *Deaths*, *Recoveries*, and *Confirmed Cases* in magnitude is indicated by a red circle for each country.

2) For a specific country chosen from the drop-down list, we display 4 graphs: Confirmed Cases, Trajectory of Confirmed Cases, Deaths, and a Forecast for the Future Number of Cases (indicated in blue from April 22 onwards).
